---
title: "Lab 5"
author: "Eva, Chloe, and Kai"
format: 
  html: 
    self-contained: true
    code-tools: true
    code-fold: true
editor: visual
execute: 
  echo: true
  include: true
  message: false
  warning: false
embed-resources: true
---

> **Goal:** Scrape information from <https://www.cheese.com> to obtain a dataset of characteristics about different cheeses, and gain deeper insight into your coding process. 🪤

```{r}
#| label: libraries
library(rvest)
library(tidyverse)
library(dplyr)
library(stringr)

```

**Part 1:** Locate and examine the `robots.txt` file for this website. Summarize what you learn from it.

The robots.txt file is located at https://www.cheese.com/robots.txt. This gives us the link to the site map which is https://www.cheese.com/sitemap.xml and that the user agent is a "\*" which means anyone can webscrape the site. The site map includes the url to all the different types of cheese in alphabetical order.

**Part 2:** Learn about the `html_attr()` function from `rvest`. Describe how this function works with a small example.

The html_attr() function gets a single attribute from the webpage. In the example, the html_elements("a") is pulling everything that has an anchor, or a hyperlink. Then the html_attr("class") is identifying which class each one is.

```{r}
#| message: false
#| label: function-use-example

url <- "https://www.cheese.com/alphabetical"
webpage <- read_html(url)
webpage |>
  html_elements("a") |>
  html_attr("class")

```

**Part 3:** (Do this alongside Part 4 below.) I used [ChatGPT](https://chat.openai.com/chat) to start the process of scraping cheese information with the following prompt:

> Write R code using the rvest package that allows me to scrape cheese information from cheese.com.

Fully document your process of checking this code. Record any observations you make about where ChatGPT is useful / not useful.

-   ChatGPT is useful in getting the names of the cheese for the first page, however it is not accurately getting the url's for the cheeses. Some of the urls it is webscraping twice which is offsetting the cheese name from the correct url.

```{r}
#| eval: false
#| label: small-example-of-getting-cheese-info

# Define the URL
url <- "https://www.cheese.com/alphabetical" #This is the url for the alphabetical list of all the cheeses on the site

# Read the HTML content from the webpage
webpage <- read_html(url) #This is useful to read in the url

# Extract the cheese names and URLs
cheese_data <- webpage %>%
  html_nodes(".cheese-item h3") %>% # We added h3 to fix the duplicates problem
  html_nodes("a") %>%
  html_attr("href") %>%
  paste0("https://cheese.com", .) # This is making the urls for the cheese

cheese_names <- webpage %>%
  html_nodes(".cheese-item h3") %>%
  html_text() # this is making the names for the cheese

# Create a data frame to store the results
cheese_df <- data.frame(Name = cheese_names,
                        URL = cheese_data,
                        stringsAsFactors = FALSE) # This is creating a dataframe with the cheese names and the urls

# Print the data frame
print(cheese_df) #This is printing the cheese_df, however the print() function does not need to be used
```

**Part 4:** Obtain the following information for **all** cheeses in the database:

-   Cheese name
-   URL for the cheese's webpage (e.g., <https://www.cheese.com/gouda/>)
-   Whether or not the cheese has a picture (e.g., [gouda](https://www.cheese.com/gouda/) has a picture, but [bianco](https://www.cheese.com/bianco/) does not)

To be kind to the website owners, please add a 1 second pause between page queries. (Note that you can view 100 cheeses at a time.)

```{r}
#| label: function-to-extract-cheese-name-url-image
url <- "https://www.cheese.com/alphabetical?per_page=100"

get_cheese <- function(url) {
  # Read the HTML content from the webpage
  webpage <- read_html(url)
  
  # Extract the cheese URLs
  cheese_data <- webpage %>%
    html_nodes(".cheese-item h3") %>% 
    html_nodes("a") %>%
    html_attr("href") %>%
    paste0("https://cheese.com", .) 
  
  # Extract the cheese names
  cheese_names <- webpage %>%
    html_nodes(".cheese-item h3") %>%
    html_text()
  
  # Extract the image links
  cheese_img <- webpage |>
    html_nodes(".cheese-item img") |>
    html_attr("src") |>
    str_replace("^/static/.*", "No image") |>
    str_replace("^/media/.*", "Yes")

  
  # Create a data frame to store the results
  cheese_df <- data.frame(Name = cheese_names,
                          URL = cheese_data,
                          Img = cheese_img,
                          stringsAsFactors = FALSE)

  # Print the data frame
  cheese_df
}


get_cheese(url)

# source for stringr cheat sheet: https://github.com/rstudio/cheatsheets/blob/main/strings.pdf

```

```{r}
#| label: fetching-all-cheese-data-from-website

# Create an empty list
all_cheeses <- c()

# Iterate across each page on the website
for(i in 1:20){
  # Construct URL for each page
  url <- paste0("https://www.cheese.com/alphabetical?per_page=100&page=", i)
  # Pause execution for one second
  Sys.sleep(1)
  # Get all URLs, cheese names, and images for each type of cheese
  cheese <- get_cheese(url) 
  # Combine the data from all of the pages
  all_cheeses <- bind_rows(all_cheeses, cheese)
}

#source for for loop: https://stackoverflow.com/questions/27153263/adding-elements-to-a-list-in-for-loop-in-r

```

**Part 5:** When you go to a particular cheese's page (like [gouda](https://www.cheese.com/gouda/)), you'll see more detailed information about the cheese. For [**just 10**]{.underline} of the cheeses in the database, obtain the following detailed information:

-   milk information
-   country of origin
-   family
-   type
-   flavour

(Just 10 to avoid overtaxing the website! Continue adding a 1 second pause between page queries.)

```{r}
get_cheese_info <- function(cheese_type){
url <- paste0("https://www.cheese.com/", cheese_type)
  webpage <- read_html(url)
  cheese_info <- webpage |>
    html_nodes("li p") |>
    html_text() |>
    unique()
  
  made_from <- str_extract(cheese_info, "(?<=Made from ).*")
  country <- str_extract(cheese_info,"(?<=Country of origin: ).*" )
  family <- str_extract(cheese_info,"(?<=Family: ).*" )
  type <- str_extract(cheese_info, "(?<=Type: ).*")
  flavour <- str_extract(cheese_info, "(?<=Flavour: ).*")
  
  cheese_info_df <- 
    data.frame(
      cheese_type = cheese_type,
      made_from = made_from,
      Country = country,
      Family = family,
      Type = type,
      Flavour = flavour
      ) |> 
    summarise_all(~ toString(na.omit(.)))
}

#source for str_extract: https://stackoverflow.com/questions/57438472/using-str-extract-in-r-to-extract-a-number-before-a-substring-with-regex
#source for sumarise_all: https://stackoverflow.com/questions/64062261/collapsing-strings-with-summarise-all
```

```{r}
for(i in 1:10){
  
}
```

**Part 6:** Evaluate the code that you wrote in terms of the [core principle of good function writing](function-strategies.qmd). To what extent does your implementation follow these principles? What are you learning about what is easy / challenging for you about approaching complex tasks requiring functions and loops?
